The classical mutual information in mean-field spin glass models

### 2015-06-29 sk_model_v17.tex

In this section we numerically confirm the analytical results of section~\ref{solution}. 
We discuss Monte Carlo (MC) data for the S-K model on the $2$-sheets booklet 
with zero external magnetic field. We focus on the internal energy $U(\omega,n,
\beta)$ 
%
\begin{equation}
\label{U-def}
U(\omega,n,\beta)\equiv-\frac{\partial}{\partial\beta}
[\log(Z(\omega,n,\beta))]. 
\end{equation}
%  
Fig.~\ref{U-MC} plots the MC data for $U(\omega,2,\beta)$ versus the inverse temperature 
$\beta$, for $\omega=1/2$. The circles, squares, and triangles are the MC results for 
different sizes, i.e., number of spins per sheet, $N=32,64,128$. The vertical dotted line 
is the critical temperature $\beta_c\approx 0.6$ of the paramagnetic-glassy transition 
(cf. Fig.~\ref{beta_c}). In the high-temperature region finite-size effects are small, 
and already for $N=64$ the MC data are indistinguishable from the thermodynamic limit 
result. Oppositely, stronger scaling corrections are visible in the low-temperature phase at 
$\beta>\beta_c$. The plus symbols in Fig.~\ref{U-MC} are the numerical extrapolations in 
the thermodynamic limit. These are obtained by fitting the finite size MC data 
to the ansatz $U/N=u_{\infty}(\omega,\beta)+c/N^{\phi}$, where 
$u_{\infty}$ is energy density in the thermodynamic limit, $c$ a fitting parameter, and 
$\phi$ the exponent of the scaling corrections. In our fits we fix $\phi=2/3$, which 
is the exponent governing the finite-size corrections of $U/N$ in 
the standard S-K model~\cite{billoire-2007,aspelmeier-2008}.

>>>>

In this section we numerically confirm the analytical results of section~\ref{solution}. 
We discuss Monte Carlo (MC) data for the S-K model on the $2$-sheets booklet 
with zero external magnetic field. The data are obtained from parallel tempering  
Monte Carlo simulations~\cite{hukushima-1996}. In the parallel tempering simulations 
$N_{\textrm{rep}}$ identical disorder realizations of the system are simulated. Each copy is at 
a different temperature in the range $\beta_{\textrm{min}}-\beta_{\textrm{max}}$. 
The standard Metropolis sweeps at 
each temperature are supplemented with parallel tempering moves, which allow 
the exchange the spin configurations between replicas with neighboring temperatures. 
In our simulations we choose $\beta_{\textrm{min}}=0.25$ and $\beta_{\textrm{max}}=2.5$, with 46 temperatures
chosen in total with equal spacing in $\beta$.
Each Monte Carlo sweep consists of $N$ single spin updates and $45$ parallel 
tempering moves. For each disorder realization we perform $10^5$ sweeps. 
The disorder average is performed over $128$ different disorder realizations.

We focus on the internal energy $U(\omega,n,
\beta)$ 
%
\begin{equation}
\label{U-def}
U(\omega,n,\beta)\equiv-\frac{\partial}{\partial\beta}
[\log(Z(\omega,n,\beta))]. 
\end{equation}
%  
Fig.~\ref{U-MC} plots the MC data for $U(\omega,2,\beta)$ versus the inverse temperature 
$\beta$, for $\omega=1/2$. The circles, squares, and triangles are the MC results for 
different sizes, i.e., number of spins per sheet, $N=32,64,128$. The vertical dotted line 
is the critical temperature $\beta_c\approx 0.6$ of the paramagnetic-glassy transition 
(cf. Fig.~\ref{beta_c}). In the high-temperature region finite-size effects are small, 
and already for $N=64$ the MC data are indistinguishable from the thermodynamic limit 
result. Oppositely, stronger scaling corrections are visible in the low-temperature phase at 
$\beta>\beta_c$. The plus symbols in Fig.~\ref{U-MC} are the numerical extrapolations in 
the thermodynamic limit. These are obtained by fitting the finite size MC data 
to the ansatz $U/N=u_{\infty}(\omega,\beta)+c/N^{\phi}$, where 
$u_{\infty}$ is energy density in the thermodynamic limit, $c$ a fitting parameter, and 
$\phi$ the exponent of the scaling corrections. In our fits we fix $\phi=2/3$, which 
is the exponent governing the finite-size corrections of $U/N$ in 
the standard S-K model~\cite{billoire-2007,aspelmeier-2008}.
